\documentclass{extarticle}
\sloppy

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PACKAGES            																						  %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[10pt]{extsizes}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage[shortlabels]{enumitem}
\usepackage{microtype} 
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{commath}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PROBLEM ENVIRONMENT         																			           %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{tcolorbox}
\tcbuselibrary{theorems, breakable, skins}
\newtcbtheorem{prob}% environment name
              {Problem}% Title text
  {enhanced, % tcolorbox styles
  attach boxed title to top left={xshift = 4mm, yshift=-2mm},
  colback=blue!5, colframe=black, colbacktitle=blue!3, coltitle=black,
  boxed title style={size=small,colframe=gray},
  fonttitle=\bfseries,
  separator sign none
  }%
  {} 
\newenvironment{problem}[1]{\begin{prob*}{#1}{}}{\end{prob*}} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% THEOREMS/LEMMAS/ETC.         																			  %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newtheorem{thm}{Theorem}
\newtheorem*{thm-non}{Theorem}
\newtheorem{lemma}[thm]{Lemma}
\newtheorem{corollary}[thm]{Corollary}
\newtheorem*{definition}{Definition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% MY COMMANDS   																						  %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\bigO}{\mathcal{O}}
\newcommand{\Real}{\mathcal{Re}}
\newcommand{\poly}{\mathcal{P}}
\newcommand{\mat}{\mathcal{M}}
\DeclareMathOperator{\Span}{span}
\newcommand{\Hom}{\mathcal{L}}
\DeclareMathOperator{\Null}{null}
\DeclareMathOperator{\Range}{range}
\newcommand{\defeq}{\vcentcolon=}
\newcommand\widebar[1]{\mathop{\overline{#1}}}
\newcommand{\restr}[1]{|_{#1}}
\DeclarePairedDelimiterX{\inp}[2]{\langle}{\rangle}{#1, #2}
\DeclarePairedDelimiter\Mod{\lvert}{\rvert}
\DeclarePairedDelimiter\Norm{\lVert}{\rVert}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SECTION NUMBERING																				           %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\renewcommand\thesection{\Alph{section}:}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% DOCUMENT START              																			           %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{\vspace{-2em}Chapter 7: Operators on Inner Product Spaces}
\author{\emph{Linear Algebra Done Right}, by Sheldon Axler}
\date{}

\begin{document}
\maketitle



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SECTION A            																			           
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Self-Adjoint and Normal Operators}

% Problem 1
\begin{problem}{1}
Suppose $n$ is a positive integer.  Define $T\in\Hom(\F^n)$ by
\begin{align*}
T(z_1, \dots, z_n) = (0, z_1, \dots, z_{n-1}).
\end{align*}
Find a formula for $T^\ast(z_1,\dots, z_n)$.
\end{problem}
\begin{proof}
Fix $(y_1,\dots, y_n)\in\F^n$.  Then for all $(z_1,\dots, z_n)\in \F^n$, we have
\begin{align*}
\inp{(z_1,\dots, z_n)}{T^\ast(y_1,\dots, y_n)} &= \inp{T(z_1,\dots, z_n)}{(y_1,\dots, y_n)}\\
&= \inp{(0, z_1,\dots, z_{n-1})}{(y_1,\dots, y_n)}\\
&= z_1y_2 + z_2y_3 + \dots + z_{n-1}y_n\\
&=\inp{(z_1,\dots, z_{n-1}, z_n)}{(y_2, \dots, y_n, 0)}.
\end{align*}
Thus $T^*$ is the left-shift operator.  That is, for all $(z_1,\dots, z_n)\in \F^n$, we have
\begin{align*}
T^\ast(z_1,\dots, z_n) = (z_2, \dots, z_n, 0),
\end{align*}
as desired.
\end{proof}

% Problem 2
\begin{problem}{2}
Suppose $T\in\Hom(V)$ and $\lambda\in\F$.  Prove that $\lambda$ is an eigenvalue of $T$ if and only if $\bar{\lambda}$ is an eigenvalue of $T^\ast$.
\end{problem}
\begin{proof}
Suppose $\lambda$ is an eigenvalue of $T$.  Then there exists $v\in V$ such that $Tv = \lambda v$.  It follows
\begin{align*}
\lambda \text{ is not an eigenvalue of }T &\iff T - \lambda I\text{ is invertible}\\
&\iff S(T - \lambda I) = (T- \lambda I)S = I \\
&~~~~~~~~~~\text{ for some }S\in\Hom(V)\\
&\iff S^\ast(T^\ast - \lambda I)^\ast = (T- \lambda I)^\ast S^\ast = I^\ast\\
&~~~~~~~~~~\text{ for some }S^\ast\in\Hom(V)\\
&\iff (T - \lambda I)^\ast\text{ is invertible}\\
&\iff T^\ast - \bar{\lambda}I \text{ is invertible}\\
&\iff \bar{\lambda} \text{ is not an eigenvalue of }T^\ast.
\end{align*}
Since the first statement and the last statement are equivalent, so too are their contrapositives.  Hence $\lambda$ is an eigenvalue of $T$ if and only if $\bar{\lambda}$ is an eigenvalue of $T^\ast$, as was to be shown.
\end{proof}

% Problem 3
\begin{problem}{3}
Suppose $T\in\Hom(V)$ and $U$ is a subspace of $V$.  Prove that $U$ is invariant under $T$ if and only if $U^\perp$ is invariant under $T^\ast$.
\end{problem}
\begin{proof}
$(\Rightarrow)$ First suppose $U$ is invariant under $T$, and let $x\in U^\perp$.  For any $u\in U$, it follows
\begin{align*}
\inp{T^\ast x}{u} &= \inp{x}{Tu}\\
&= 0,
\end{align*}
where the second equality follows since $Tu\in U$ (by hypothesis).  Thus $T^\ast x\in U^\perp$ for all $x\in U^\perp$.  That is, $U^\perp$ is invariant under $T^\ast$.\\
\indent $(\Leftarrow)$ Now suppose $U^\perp$ is invariant under $T^\ast$, and let $y\in U$.  For any $u'\in U^\perp$, it follows
\begin{align*}
\inp{T y}{u'} &= \inp{y}{T^\ast u'}\\
&= 0,
\end{align*}
where the second equality follows since $T^\ast u'\in U^\perp$ (by hypothesis).  Thus $T y\in U$ for all $y\in U$.  That is, $U$ is invariant under $T$, completing the proof.
\end{proof}

% Problem 5
\begin{problem}{5}
Prove that 
\begin{align*}
\dim\Null T^\ast = \dim\Null T + \dim W - \dim V
\end{align*}
and
\begin{align*}
\dim\Range T^* = \dim\Range T
\end{align*}
for every $T\in\Hom(V, W)$.
\end{problem}
\begin{proof}
Let $T\in\Hom(V, W)$.  Notice
\begin{align*}
\dim\Null T^\ast &= \dim\left(\Range T\right)^\perp\\
&=\dim W - \dim\Range T\\
&=\dim W + \dim\Null T - \dim V,
\end{align*}
where the first equality follows by 7.7(a), the second equality follows by 6.50, and the third equality follows by the Fundamental Theorem of Linear Maps.  Next notice
\begin{align*}
\dim\Range T^\ast &= \dim\left(\Null T\right)^\perp\\
&= \dim V - \dim\Null T\\
&= \dim \Range T,
\end{align*}
where the first equality follows by 7.7(b), and the second and third equalities follow again by the same theorems above.
\end{proof}

% Problem 7
\begin{problem}{7}
Suppose $S,T\in\Hom(V)$ are self-adjoint.  Prove that $ST$ is self-adjoint if and only if $ST=TS$.
\end{problem}
\begin{proof}
$(\Rightarrow)$ Suppose $ST$ is self-adjoint.  We have
\begin{align*}
ST &= (ST)^\ast\\
&= T^\ast S^\ast\\
&=TS,
\end{align*}
where the second equality follows by 7.6(e).\\
\indent $(\Leftarrow)$ Conversely, suppose $ST = TS$.  It follows
\begin{align*}
(ST)^\ast &= (TS)^\ast\\
&= S^\ast T^\ast,
\end{align*}
where the second equality again follows by 7.6(e), completing the proof.
\end{proof}

% Problem 9
\begin{problem}{9}
Suppose $V$ is a complex inner product space with $V\neq\{0\}$.  Show that the set of self-adjoint operators on $V$ is not a subspace of $\Hom(V)$.
\end{problem}
\begin{proof}
Let $\mathcal{A}$ denote the set of self-adjoint operators on $V$, and suppose $T\in\mathcal{A}$.  By 7.6(b), notice $(iT)^\ast = -iT^\ast$, so that $\mathcal{A}$ is not closed under scalar multiplication.  Thus $\mathcal{A}$ is not a subspace of $\Hom(V)$.
\end{proof}

% Problem 11
\begin{problem}{11}
Suppose $P\in\Hom(V)$ is such that $P^2 = P$.  Prove that there is a subspace $U$ of $V$ such that $P = P_U$ if and only if $P$ is self-adjoint.
\end{problem}
\begin{proof}
$(\Rightarrow)$ First suppose there is a subspace $U\subseteq V$ such that $P = P_U$, and let $v_1,v_2\in V$.  It follows
\begin{align*}
\inp{Pv_1}{v_2} &= \inp{u_1}{u_2 + w_2}\\
&= \inp{u_1}{u_2} + \inp{u_1}{w_2}\\
&= \inp{u_1}{u_2}\\
&= \inp{u_1}{u_2} + \inp{w_1}{u_2}\\
&= \inp{u_1 + w_1}{u_2}\\
&= \inp{v_1}{Pv_2},
\end{align*}
and thus $P = P^\ast$.\\
\indent $(\Leftarrow)$ Conversely, suppose $P = P^\ast$.  Let $v\in V$.  Notice $P(v - Pv)= Pv - P^2v = 0$, and hence $v - Pv\in\Null P$.  By 7.7(c), we know $\Null P = \left(\Range T^\ast\right)^\perp$.  By hypothesis, $P$ is self-adjoint, and hence we have $v-Pv \in \left(\Range T\right)^\perp$.  Notice we may write
\begin{align*}
v = Pv + (v - Pv),
\end{align*}
where $Pv \in \Range P$ and $v-Pv \in \left(\Range T\right)^\perp$.  Let $U = \Range P$.  Since the above holds for all $v\in V$, we conclude $P = P_U$, and the proof is complete.
\end{proof}

% Problem 13
\begin{problem}{13}
Give an example of an operator $T\in\Hom(\C^4)$ such that $T$ is normal but not self-adjoint.
\end{problem}
\begin{proof}
Let $T$ be the operator on $\C^4$ whose matrix with respect to the standard basis is
\begin{align*}
\begin{bmatrix}
2 & -3 & 0 & 0\\
3 &  2 & 0 & 0\\
0 &  0 & 0 & 0\\
0 &  0 & 0 & 0
\end{bmatrix}.
\end{align*} 
We claim $T$ is normal and not self-adjoint.  To see that $T$ is not self-adjoint, notice that the entry in row $2$, column $1$ does not equal the complex conjugate of the entry in row $1$ column $2$.\\
\indent Next, notice
\begin{align*}
\mat(TT^\ast) &= 
\begin{bmatrix}
2 & -3 & 0 & 0\\
3 &  2 & 0 & 0\\
0 &  0 & 0 & 0\\
0 &  0 & 0 & 0
\end{bmatrix}
\begin{bmatrix}
2  & 3 & 0 & 0\\
-3 & 2 & 0 & 0\\
0  & 0 & 0 & 0\\
0  & 0 & 0 & 0
\end{bmatrix}
= 
\begin{bmatrix}
13  & 0 & 0 & 0\\
0 & 13 & 0 & 0\\
0  & 0 & 0 & 0\\
0  & 0 & 0 & 0
\end{bmatrix}
\end{align*}
and 
\begin{align*}
\mat(T^\ast T) &= 
\begin{bmatrix}
2 & 3 & 0 & 0\\
-3 &  2 & 0 & 0\\
0 &  0 & 0 & 0\\
0 &  0 & 0 & 0
\end{bmatrix}
\begin{bmatrix}
2  & -3 & 0 & 0\\
3 & 2 & 0 & 0\\
0  & 0 & 0 & 0\\
0  & 0 & 0 & 0
\end{bmatrix}
= 
\begin{bmatrix}
13  & 0 & 0 & 0\\
0 & 13 & 0 & 0\\
0  & 0 & 0 & 0\\
0  & 0 & 0 & 0
\end{bmatrix},
\end{align*}
and hence $TT^\ast$ and $T^\ast T$ have the same matrix.  Thus $TT^\ast = T^\ast T$, and $T$ is normal.   
\end{proof}

% Problem 15
\begin{problem}{15}
Fix $u,x\in V$.  Define $T\in\Hom(V)$ by
\begin{align*}
Tv = \inp{v}{u}x
\end{align*}
for every $v\in V$.
\begin{itemize}[(a)]
\item Suppose $\F = \R$.  Prove that $T$ is self-adjoint if and only if $u,x$ is linearly dependent.
\item Prove that $T$ is normal if and only if $u,x$ is linearly dependent.
\end{itemize}
\end{problem}
\begin{proof}
We first derive a useful formula for $T^\ast$ which we'll use in both (a) and (b).  Let $w_1,w_2\in V$ and notice
\begin{align*}
\inp{w_1}{T^\ast w_2} &= \inp{Tw_1}{w_2}\\
&= \inp{\inp{w_1}{u}x}{w_2}\\
&= \inp{w_1}{u}\inp{x}{w_2}\\
&= \inp{w_1}{\widebar{\inp{x}{w_2}}u}\\
&= \inp{w_1}{\inp{w_2}{x}u},
\end{align*}
and thus $T^\ast w_2 = \inp{w_2}{x}u$.  Since $w_2$ was arbitrary, we may rewrite this as $T^\ast v = \inp{v}{x}u$ for all $v\in V$.
\begin{enumerate}[(a), listparindent=1.5em]
\item $(\Rightarrow)$ Suppose $T$ is self-adjoint.  Then we have
\begin{align*}
\inp{v}{u}x - \inp{v}{x}u = Tv - T^\ast v = 0
\end{align*}
for all $v\in V$.  In particular, we have
\begin{align*}
\inp{u}{u}x - \inp{u}{x}u = 0.
\end{align*}
We may assume both $u$ and $x$ are nonzero, for otherwise there is nothing to prove.  Hence $\inp{u}{u}\neq 0$, which forces $\inp{u}{x}$ to be nonzero as well, and thus the equation above shows $u,x$ is linearly dependent.\\
\indent $(\Leftarrow)$ Conversely, suppose $u,x$ is linearly dependent.  We may again assume both $u$ and $x$ are nonzero, for otherwise $T=0$, which is self-adjoint.  Thus there exists a nonzero $\alpha\in\R$ such that $u = \alpha x$.  It follows
\begin{align*}
Tv &= \inp{v}{u}x\\
&= \inp{v}{\alpha x}\frac{1}{\alpha} u\\
&= \inp{v}{x}u\\
&= T^\ast,
\end{align*}
and thus $T$ is self-adjoint, completing the proof.
\item $(\Rightarrow)$ Suppose $T$ is normal and let $v\in V$.  It follows
\begin{align*}
\inp{\inp{v}{u}x}{x}u &= T^\ast(\inp{v}{u}x)\\
&= T^\ast Tv\\
&= TT^\ast v\\
&= T(\inp{v}{x}u)\\
&= \inp{\inp{v}{x}u}{u}x.
\end{align*}
We may assume both $u$ and $x$ are nonzero, for otherwise there is nothing to prove.  Since the above holds for $v = u$, we may conclude $\inp{\inp{v}{u}x}{x} \neq 0$, which also forces $\inp{\inp{v}{x}u}{u} \neq 0$.  Thus $u, x$ is linearly dependent.\\
\indent $(\Leftarrow)$ Conversely, suppose $u,x$ is linearly dependent.  We may again assume both $u$ and $x$ are nonzero, for otherwise $T = 0$, which is normal.  Thus there exists a nonzero $\alpha\in\R$ such that $u = \alpha x$.  It follows
\begin{align*}
T^\ast Tv &= T^\ast(\inp{v}{u}x)\\
&= \inp{\inp{v}{u}x}{x}u\\
&= \left\langle\inp{v}{\alpha x}\frac{1}{\alpha} u, \frac{1}{\alpha}u\right\rangle \alpha x\\
&= \inp{\inp{v}{x}u}{u}x\\
&= T(\inp{v}{x}u)\\
&= TT^\ast v,
\end{align*}
and thus $T$ is normal, completing the proof. \qedhere
\end{enumerate}
\end{proof}

% Problem 16
\begin{problem}{16}
Suppose $T\in\Hom(V)$ is normal.  Prove that
\begin{align*}
\Range T = \Range T^\ast.
\end{align*}
\end{problem}
\begin{proof}
Suppose $T\in\Hom(V)$ is normal.  We first prove $\Null T = \Null T^\ast$.  It follows
\begin{align*}
v\in\Null T &\iff Tv = 0\\
&\iff \norm{Tv} = 0\\
&\iff \norm{T^\ast v} = 0\\
&\iff T^\ast v = 0\\
&\iff v\in\Null T^\ast,
\end{align*}
where the third equivalence follows by 7.20, and indeed we have $\Null T = \Null T^\ast$.  This implies $(\Null T)^\perp = (\Null T^\ast)^\perp$,
and by 7.7(b) and 7.7(c), this is equivalent to $\Range T^\ast = \Range T$, as desired.
\end{proof}

% Problem 17
\begin{problem}{17}
Suppose $T\in\Hom(V)$ is normal.  Prove that
\begin{align*}
\Null T^k = \Null T \quad \text{and} \quad \Range T^k = \Range T
\end{align*}
for every positive integer $k$.
\end{problem}
\begin{proof}
To show $\Null T^k = \Null T$, we first prove $\Null T^k = \Null T^{k + 1}$ for all $k\in\Z^+$.  Let $m\in\Z^+$.  If $m = 1$, there's nothing to prove, so we may assume $m > 1$.  Clearly, if $v\in\Null T^m$, then $v\in\Null T^{m+1}$, and hence $\Null T^m \subseteq\Null T^{m+1}$.  Next, suppose $v\in\Null T^{m + 1}$.  Then $T(T^m v)=0$, and hence $T^mv\in\Null T$.  By Problem 16, this implies $T^mv\in\Null T^\ast$, and by 7.7(a) we have $T^m\in(\Range T)^\perp$.  Since of course $T^mv\in\Range T$ as well, we must have $T^mv = 0$.  Thus $v \in \Null T^m$, and therefore $\Null T^{m+1} \subseteq \Null T^m$.  Thus $\Null T^m = \Null T^{m + 1}$.  Since $m$ was arbitrary, this implies $\Null T^k = \Null T$ for all $k\in\Z^+$, as desired.\\
\indent Now we will show $\Range T^k = \Range T$ for all $k\in\Z^+$.  Let $n\in\Z^+$.  If $n=1$, there's nothing to prove, so we may assume $n>1$.  Suppose $w\in \Range T^{n}$.  Then there exists $v\in V$ such that $T^nv = w$, and hence $T(T^{n-1}v) = w$, so that $w\in\Range T$ as well and we have $\Range T^n\subseteq \Range T$.  Next, notice 
\begin{align*}
\dim \Range T^n &= \dim V - \dim \Null T^n\\
&= \dim V - \dim\Null T\\
&= \dim \Range T,
\end{align*}
where the second equality follows from the previous paragraph.  Since $\Range T^n$ is a subspace of $\Range T$ of the same dimension, it must equal $\Range T$.  And since $n$ was arbitrary, we conclude $\Range T^k = \Range T$ for all $k\in\Z^+$, completing the proof.
\end{proof}

% Problem 19
\begin{problem}{19}
Suppose $T\in\Hom(\C^3)$ is normal and $T(1, 1, 1) = (2, 2, 2)$.  Suppose $(z_1,z_2,z_3)\in\Null T$.  Prove that $z_1 + z_2 + z_3 = 0$.
\end{problem}
\begin{proof}
By Problem 16, $\Null T = \Null T^\ast$, hence $T^\ast(z_1, z_2, z_3) = 0$.  Therefore, we have
\begin{align*}
2(z_1 + z_2 + z_3) &= \inp{(2, 2, 2)}{(z_1, z_2, z_3)}\\
&= \inp{T(1, 1, 1)}{(z_1, z_2, z_3)} \\
&= \inp{(1, 1, 1)}{T^\ast(z_1, z_2, z_3)}\\
&= \inp{(1, 1, 1)}{(0, 0, 0)}\\
&= 0,
\end{align*}
and so $z_1 + z_2 + z_3 = 0$, as was to be shown. 
\end{proof}

% Problem 21
\begin{problem}{21}
Fix a positive integer $n$.  In the inner product space of continuous real-valued functions on $[-\pi, \pi]$ with inner product
\begin{align*}
\inp{f}{g} = \int_{-\pi}^\pi f(x)g(x)dx,
\end{align*}
let 
\begin{align*}
V = \Span(1, \cos x, \cos 2x, \dots, \cos nx, \sin x, \sin 2x, \dots, \sin nx).
\end{align*}
\begin{enumerate}[(a)]
\item Define $D\in\Hom(V)$ by $Df = f'$.  Show that $D^\ast = -D$.  Conclude that $D$ is normal but not self-adjoint.
\item Define $T\in\Hom(V)$ by $Tf = f''$.  Show that $T$ is self-adjoint.
\end{enumerate}
\end{problem}
\begin{proof}
From Problem 4 of 6B, recall that
\begin{align*}
\frac{1}{\sqrt{2\pi}}, \frac{\cos x}{\sqrt{\pi}}, \frac{\cos 2x}{\sqrt{\pi}}, \dots, \frac{\cos nx}{\sqrt{\pi}}, \frac{\sin x}{\sqrt{\pi}}, \frac{\sin 2x}{\sqrt{\pi}}, \dots, \frac{\sin nx}{\sqrt{\pi}}
\end{align*}
is an orthonormal list, and hence it is an orthonormal basis of $V$.  
\begin{enumerate}[(a)]
\item For $k = 1,\dots, n$, define
\begin{align*}
e_k = \frac{\cos(kx)}{\sqrt{\pi}}\quad\text{and}\quad f_k= \frac{\sin(kx)}{\sqrt{\pi}}.
\end{align*}
Notice
\begin{align*}
De_k = -\frac{k\sin(kx)}{\sqrt{\pi}} = -kf_k\quad\text{and}\quad Df_k = \frac{k\cos(kx)}{\sqrt{\pi}} = ke_k,
\end{align*}
and thus, for any $v,w\in V$, it follows
\begin{align*}
\inp{v}{D^\ast w} &= \inp{Dv}{w}\\
&= \left\langle D\left(\left\langle v, \frac{1}{\sqrt{2\pi}}\right\rangle \frac{1}{\sqrt{2\pi}}+\sum_{k=1}^n\left(\inp{v}{e_k}e_k + \inp{v}{f_k}f_k\right)\right), w\right\rangle\\
&= \left\langle \sum_{k=1}^n\left(-k\inp{v}{e_k}f_k + k\inp{v}{f_k}e_k\right), w\right\rangle\\
&= -\sum_{k = 1}^nk\inp{v}{e_k}\inp{f_k}{w} + \sum_{k = 1}^nk\inp{v}{f_k}\inp{e_k}{w}\\
&= -\sum_{k= 1}^nk\inp{w}{f_k}\inp{v}{e_k} +  \sum_{k = 1}^nk\inp{w}{e_k}\inp{v}{f_k}\\
&= \sum_{k = 1}^nk\inp{w}{e_k}\inp{v}{f_k} - \sum_{k= 1}^nk\inp{w}{f_k}\inp{v}{e_k}\\
&= \left\langle v, \sum_{k=1}^nk\inp{w}{e_k}f_k \right\rangle - \left\langle v, \sum_{k=1}^nk\inp{w}{f_k}e_k \right\rangle\\
&= \left\langle v, \sum_{k=1}^n\left(k\inp{w}{e_k}f_k - k\inp{w}{f_k}e_k \right)\right\rangle\\
&= \left\langle v,  -D\left(\left\langle w, \frac{1}{\sqrt{2\pi}}\right\rangle \frac{1}{\sqrt{2\pi}}+\sum_{k=1}^n\left(\inp{w}{e_k}e_k + \inp{w}{f_k}f_k\right)\right)\right\rangle\\
&= \inp{v}{-Dw},
\end{align*}
and thus $D^\ast = -D$, showing that $D$ is not self-adjoint.  Moreover, notice that this implies
\begin{align*}
DD^\ast = D(-D) = -DD = (D^\ast)D = D^\ast D,
\end{align*}
so that $D$ is normal, completing the proof.

\item Notice $T = D^2$, and hence
\begin{align*} 
T^\ast = (DD)^\ast = D^\ast D^\ast = (-D)(-D) = D^2  = T.
\end{align*}
Thus $T$ is self-adjoint. \qedhere
\end{enumerate}
\end{proof}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SECTION B           																			           
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The Spectral Theorem}

% Problem 1
\begin{problem}{1}
True or false (and give a proof of your answer): There exists $T\in\Hom(\R^3)$ such that $T$ is not self-adjoint (with respect to the usual inner product) and such that there is a basis of $\R^3$ consisting of eigenvectors of $T$.
\end{problem}
\begin{proof}
The statement is true.  To see this, consider the linear operator $T$ defined by its action on the basis $(1, 0, 0), (0, 1, 0), (0, 1, 1)$:
\begin{align*}
T(1, 0, 0) &= (0, 0, 0)\\
T(0, 1, 0) &= (0, 0, 0)\\
T(0, 1, 1) &= (0, 1, 1).
\end{align*}
Notice $T(1, 0, 0) = 0\cdot (1, 0, 0)$ and $T(0, 1, 0) = 0\cdot (0, 1, 0)$, so that $(1, 0, 0)$ and $(0, 1, 0)$ are eigenvectors with eigenvalue $0$.  Also, $(0, 1, 1)$ is an eigenvector with eigenvalue $1$.  Thus $(1, 0, 0,), (0, 1, 0), (0, 1, 1)$ is a basis of $\R^3$ consisting of eigenvectors of $T$.  That $T$ is not self-adjoint follows from the contrapositive of 7.22, since $(0, 1, 0)$ and $(0, 1, 1)$ correspond to distinct eigenvalues yet they are not orthogonal.
\end{proof}

% Problem 3
\begin{problem}{3}
Give an example of an operator $T\in\Hom(\C^3)$ such that $2$ and $3$ are the only eigenvalues of $T$ and $T^2 - 5T + 6I \neq 0$.
\end{problem}
\begin{proof}
Define $T\in\Hom(\C^3)$ by its action on the standard basis:
\begin{align*}
Te_1 &= 2e_2\\
Te_2 &= e_1 + 2e_2\\
Te_3 &= 3e_3.
\end{align*}
Then 
\begin{align*}
\mat(T) = \begin{bmatrix}2 & 1 & 0\\ 0 & 2 & 0\\ 0 & 0 & 3\end{bmatrix}.
\end{align*}
By 5.32, the only eigenvalues of $T$ are the entries on the diagonal: $2$ and $3$.  Now notice
\begin{align*}
(T^2 - 5T + 6I)e_2 &= (T - 3I)(T - 2I)e_2\\
&= (T - 3I)(Te_2 - 2e_2)\\
&= (T - 3I)(e_1 + 2e_2 - 2e_2)\\
&= (T - 3I)e_1\\
&= Te_1 - 3e_1\\
&= -e_1,
\end{align*}
so that $T^2 - 5T + 6I\neq 0$.  Thus $T$ is an operator of the desired form.
\end{proof}

% Problem 5
\begin{problem}{5}
Suppose $\F=\R$ and $T\in\Hom(V)$.  Prove that $T$ is self-adjoint if and only if all pairs of eigenvectors corresponding to distinct eigenvalues of $T$ are orthogonal and 
\begin{align*}
V = E(\lambda_1, T)\oplus \dots \oplus E(\lambda_m, T),
\end{align*}
where $\lambda_1,\dots,\lambda_m$ denote the distinct eigenvalues of $T$.
\end{problem}
\begin{proof}
$(\Leftarrow)$ Suppose all pairs of eigenvectors corresponding to distinct eigenvalues of $T$ are orthogonal and 
\begin{align*}
V = E(\lambda_1, T)\oplus \dots \oplus E(\lambda_m, T),
\end{align*}
where $\lambda_1,\dots,\lambda_m$ denote the distinct eigenvalues of $T$.  By 5.41, $V$ has a basis consisting of eigenvectors of $T$.  Dividing each element of the basis by its norm produces an orthonormal basis consisting of eigenvectors of $T$.  By the Real Spectral Theorem, $T$ is self-adjoint, as desired.\\
\indent $(\Rightarrow)$ Conversely, suppose $T$ is self-adjoint as suppose $v_1,v_2\in V$ are eigenvectors of $T$ corresponding to eigenvalues $\lambda_1,\lambda_2\in\R$ such that $\lambda_1\neq\lambda_2$.  It follows
\begin{align*}
0 &= \inp{Tv_1}{v_2} - \inp{v_1}{Tv_2}\\
&= \inp{\lambda_1 v_1}{v_2} - \inp{v_1}{\lambda_2 v_2}\\
&= \lambda_1\inp{v_1}{v_2} - \widebar{\lambda_2}\inp{v_1}{v_2}\\
&= \lambda_1\inp{v_1}{v_2} - \lambda_2\inp{v_1}{v_2}\\
&= (\lambda_1 - \lambda_2)\inp{v_1}{v_2}.
\end{align*}
Since $\lambda_1\neq \lambda_2$, it must be that $\inp{v_1}{v_2}=0$.  Thus all pairs of eigenvectors corresponding to distinct eigenvalues of $T$ are orthogonal.  By the Real Spectral Theorem, since $T$ is self-adjoint, $T$ is diagonalizable.  And by 5.34, this implies
\begin{align*}
V = E(\lambda_1, T)\oplus \dots \oplus E(\lambda_m, T),
\end{align*}
where $\lambda_1,\dots,\lambda_m$ denote the distinct eigenvalues of $T$, completing the proof.
\end{proof}

% Problem 6
\begin{problem}{6}
Prove that a normal operator on a complex vector space is self-adjoint if and only if all its eigenvalues are real.
\end{problem}
\begin{proof}
Let $T$ be a normal operator on a complex vector space, $V$.\\
\indent $(\Rightarrow)$ Suppose $T$ is self-adjoint.  Then by 7.13, all eigenvalues of $T$ are real.\\
\indent $(\Leftarrow)$ Conversely, suppose all eigenvalues of $T$ are real.  By the Complex Spectral Theorem, there exists an orthonormal basis $v_1,\dots, v_n$ of $V$ consisting of eigenvectors of $T$.  Thus there exist $\lambda_1,\dots, \lambda_n\in\R$ such that $Tv_k = \lambda_k v_k$ for $k = 1,\dots, n$.  Thus $\mat(T)$ is diagonal, and all entries along the diagonal are real.  Therefore $\mat(T)$ equals the conjugate transpose of $\mat(T)$.  By 7.10, this implies $\mat(T) = \mat(T^\ast)$, and we conclude $T = T^\ast$, so that $T$ is indeed self-adjoint.
\end{proof}

% Problem 7
\begin{problem}{7}
Suppose $V$ is a complex inner product space and $T\in\Hom(V)$ is a normal operator such that $T^9 = T^8$.  Prove that $T$ is self-adjoint and $T^2 = T$.   
\end{problem}
\begin{proof}
By the Complex Spectral Theorem, since $T$ is normal, $V$ has an orthonormal basis $v_1,\dots, v_n$ consisting of eigenvectors of $T$.  Let $\lambda_1,\dots, \lambda_n\in\C$ be the corresponding eigenvalues, so that
\begin{align*}
Tv_k = \lambda_k v_k
\end{align*}
for $k = 1,\dots, n$.  Repeatedly applying $T$ to both sides of the equation above $8$ times yields
\begin{align*}
T^9v_k = (\lambda_k)^9 v_k\quad\text{and}\quad T^8v_k = (\lambda_k)^8 v_k.
\end{align*}
Since $T^9 = T^8$, we conclude $(\lambda_k)^9 = (\lambda_k)^8$ and thus $\lambda_k\in\{0, 1\}$.  In particular, all eigenvalues of $T$ are real, hence by Problem 6 we have that $T$ is self-adjoint.\\
\indent To see that $T^2 = T$, notice 
\begin{align*}
T^2v_k &= (\lambda_k)^2v_k\\
&= \lambda_k v_k\\
&=Tv_k,
\end{align*}
where the second equality follows from the fact that $\lambda_k\in\{0,1\}$, and the proof is complete.
\end{proof}

% Problem 9
\begin{problem}{9}
Suppose $V$ is a complex inner product space.  Prove that every normal operator on $V$ has a square root.  (An operator $S\in\Hom(V)$ is called a \textbf{\textit{square root}} of $T\in\Hom(V)$ if $S^2 = T$.)
\end{problem}
\begin{proof}
Suppose $T\in\Hom(V)$ is normal.  By the Complex Spectral Theorem, $V$ has an orthonormal basis $v_1,\dots, v_n$ consisting of eigenvectors of $T$.  Let $\lambda_1,\dots, \lambda_n\in\C$ be the corresponding eigenvalues, so that
\begin{align*}
Tv_k = \lambda_k v_k
\end{align*}
for $k = 1,\dots, n$.  Define $S\in\Hom(V)$ by its action on this basis:
\begin{align*}
Sv_k = \sqrt{\lambda_k}v_k,
\end{align*}
choosing the complex square root $\sqrt{\lambda_k}$ by some definite rule.  Let $v\in V$.  Then there exist $\alpha_1,\dots, \alpha_n\in\C$ such that $v = \alpha_1v_1 + \dots + \alpha_nv_n$.  It follows
\begin{align*}
S^2 v &= S^2( \alpha_1v_1 + \dots + \alpha_nv_n)\\
&= S\left(\alpha_1\sqrt{\lambda_1}v_1 + \dots + \alpha_n\sqrt{\lambda_n}v_n\right)\\
&= \alpha_1\lambda_1v_1 + \dots + \alpha_n\lambda_n v_n\\
&= \alpha_1Tv_1 + \dots + \alpha_nTv_n\\
&= T( \alpha_1v_1 + \dots + \alpha_nv_n)\\
&= Tv.
\end{align*}
Thus $S^2 = T$, and indeed $T$ has a square root, as was to be shown.
\end{proof}

\begin{problem}{11}
Prove or give a counterexample: every self-adjoint operator on $V$ has a cube root.  (An operator $T\in\Hom(V)$ is called a \textbf{\textit{cube root}} of $T\in\Hom(V)$ if $S^3 = T$.)
\end{problem}
\begin{proof}
Suppose $T\in\Hom(V)$ is self-adjoint.  Regardless of whether $\F=\R$ or $\F =\R$, both Spectral Theorems imply that $V$ has an orthonormal basis $v_1,\dots, v_n$ consisting of eigenvectors of $T$.  By 7.13, all eigenvalues of $T$ are real.  So let $\lambda_1,\dots, \lambda_n\in\R$ be the eigenvalues corresponding to $v_1,\dots, v_n$, so that
\begin{align*}
Tv_k = \lambda_k v_k
\end{align*}
for $k = 1,\dots, n$.  Define $S\in\Hom(V)$ by its action on this basis:
\begin{align*}
Sv_k = (\lambda_k)^\frac{1}{3}v_k,
\end{align*}
Let $v\in V$.  Then there exist $\alpha_1,\dots, \alpha_n\in\C$ such that $v = \alpha_1v_1 + \dots + \alpha_nv_n$.  It follows
\begin{align*}
S^3 v &= S^3( \alpha_1v_1 + \dots + \alpha_nv_n)\\
&= S^2\left(\alpha_1(\lambda_1)^\frac{1}{3}v_1 + \dots + \alpha_n(\lambda_n)^\frac{1}{3}v_n\right)\\
&= S\left(\alpha_1(\lambda_1)^\frac{2}{3}v_1 + \dots + \alpha_n(\lambda_n)^\frac{2}{3} v_n\right)\\
&= \alpha_1\lambda_1v_1 + \dots + \alpha_n\lambda_n v_n\\
&= \alpha_1Tv_1 + \dots + \alpha_nTv_n\\
&= T( \alpha_1v_1 + \dots + \alpha_nv_n)\\
&= Tv.
\end{align*}
Thus $S^3 = T$, and indeed $T$ has a cube root.  Thus, all self-adjoint operators on a finite-dimensional inner product space have a cube root.
\end{proof}

% Problem 13
\begin{problem}{13}
Give an alternative proof of the Complex Spectral Theorem that avoids Schur's Theorem and instead follows the pattern of the proof of the Real Spectral Theorem.
\end{problem}
\begin{proof}
The equivalence of statements (a) and (b) follows immediately from 5.41.  We proceed by first proving (c) implies (a) and then prove (a) implies (a).\\
\indent Suppose (c) holds, so that $T$ has a diagonal matrix with respect to some orthonormal basis of $V$.  The matrix of $T^\ast$ (with respect to the same basis) is obtained by taking the conjugate transpose of the matrix of $T$; hence $T^\ast$ also has a diagonal matrix.  Any two diagonal matrices commute; thus $T$ commutes with $T^\ast$, which means that $T$ is normal.  That is, (a) holds.\\
\indent We will prove that (a) implies (b) by induction on $\dim V$.  For our base case, suppose $\dim V= 1$.  Since 5.21 guarantees the existence of an eigenvector of $T$, clearly (b) is true.  Next assume that $\dim V > 1$ and that (a) implies (b) for all complex inner product spaces of smaller dimension.\\
\indent Suppose (a) holds, so that $T$ is normal.  Let $u$ be an eigenvector of $T$ with $\norm{u} = 1$, and set $U = \Span(u)$.  We claim $U$ is invariant under $T$.  To see this, suppose $v\in U$.  Then there exists $\alpha\in\C$ such that $v = \alpha u$.  It follows
\begin{align*}
Tv = T(\alpha u) = \alpha Tu \in U,
\end{align*}
and hence $U$ is indeed invariant under $T$.  By Problem 3 of 7A, this implies that $U^\perp$ is invariant under $T^\ast$.
\end{proof}
\end{document}